### 2019-04-15 paper/paper.tex
comparing similar packages

@@

To better understand the evolution of package popularity,
we investigate the dynamics of the top rankings over time.
While figure \ref{ranksByYear} demonstrate that package popularity
appears to be relatively stable, we can examine the number of packages
entering (and therefore exiting) the top \code{n} packages per year in
order to obtain a better view of the ecosystem as a whole.
Table \ref{numEnteringTop} depicts amount of newcomers to the top
\code{npm} ranks each year, further supporting the observation that
core \code{npm} package popularity is becoming more stable as the 
ecosystem matures.

\subsubsection{Comparing Popularities}
[NEEDS MORE DATA]

@@

>>>>

To better understand the evolution of package popularity,
we investigate the dynamics of the top rankings over time.
While figure \ref{ranksByYear} demonstrate that package popularity
appears to be relatively stable, we can examine the number of packages
entering (and therefore exiting) the top \code{n} packages per year in
order to obtain a better view of the ecosystem as a whole.
Table \ref{numEnteringTop} depicts the amount of newcomers to the top
\code{npm} ranks each year, further supporting the observation that
core \code{npm} package popularity is becoming more stable as the 
ecosystem matures.

@@

\subsubsection{Comparing the Popularity of Similar Packages}

@@

One of the significant benefits of being able to determine
\code{npm} ranks over time is that it allows for the comparison
of similar packages against each other at an objective level.
Figure \ref{selectPackages} shows the npm ranks of selected 
utility packages, as chosen in the original paper \cite{Wittern:2016}.
One of these packages, \code{underscore}, is among the oldest \code{npm} 
utility packages, and the rest have been selected for being
typical alternatives to the \code{underscore} package. Some of these packages,
such as \code{lodash}, are directly or indirectly results of forks from the
\code{underscore} repository. While \code{lodash} has kept up and even surpassed
\code{underscore} in popularity, the majority of newer alternatives are unable
to consistently compete. Calculating ranks for similar groups of packages such as
this allow us to isolate notable, successful packages across the entire span of
the ecosystem's history, as well as evaluate the persistence of the most popular
core packages over time. In the example group of packages presented in Figure \ref{selectPackages},
we can observe that the package established early in the ecosystem's life-cycle
is well-positioned to maintain a significant level of popularity, while the majority of
other packages tend to eventually decline unless they provide something exceptional,
such as \code{lodash} providing API compatibility with \code{underscore}\footnote{https://lodash.com/}.
